MSHS COVID-19 Vaccinations

### 2022-02-04 Combined Dashboard Arrived and Sched Appts.Rmd
Update analysis reference file.

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2022-01-10.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2022-01-10.xlsx"),
                           sheet = "Pod Mappings Simple")

@@

>>>>

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2022-01-18.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2022-01-18.xlsx"),
                           sheet = "Pod Mappings Simple")

@@

#### {-}
<h5><i>Appointments at school-based practices included in MSH volume.</i></h5>
